\documentclass[12pt]{report}

\providecommand{\E}[1]{\ensuremath{\times 10^{#1}}}
\usepackage{graphicx}% Include figure files
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\usepackage{natbib}
%\bibliographystyle{ieeetr}
\bibliographystyle{agufull08}
\setcitestyle{authoryear, square}

\usepackage{cleveref}
%\usepackage{caption}
\usepackage{subcaption}





% Vectors in bold font instead of line over
\renewcommand{\vec}[1]{\mathbf{#1}}
% Math-mode vector alternative (greek symbols)
\newcommand{\mvec}[1]{\boldsymbol{#1}}

% units in math mode
\newcommand{\unit}[1]{\quad[\mathrm{#1}]}

% Big fractions
\newcommand{\bigfrac}[2]{\ensuremath{\frac{\displaystyle #1}{\displaystyle #2}}}


% Exponential:
\renewcommand{\exp}[1]{e^{#1}}
\usepackage{suthesis-2e}
    \specialthesis

\dept{Electrical Engineering}


    \begin{document}
    \title{Global and Seasonal Effects of\\
            Lightning-Induced Electron Precipitation}
    \author{Austin Patrick Sousa}
    \principaladviser{Prof. Sigrid Close}
    \firstreader{Prof. Robert Marshall, University of Colorado Boulder}
    \secondreader{Prof. Antony Fraser-Smith} 
    \beforepreface
    \prefacesection{Preface}
        This thesis tells you all you need to know about...
    \prefacesection{Acknowledgments}
        \input{chapters/acknowledgments}
    \afterpreface
 
    \chapter{Introduction}
    	\input{chapters/introduction}

    \chapter[Physics and Methods]{Background Physics and Description of Methods}
    	\input{chapters/physics}



    \chapter{VLF energy in the Near-Earth Environment}
    	\input{chapters/lightning}

    \chapter{3D Modeling of LEP}
  	\input{chapters/3dWIPP}

    \chapter{Global and Seasonal Estimates of LEP}
    	\input{chapters/global_estimates}

    \chapter{Satellite Instrumentation for LEP Measurement}
    	\input{chapters/VPM}

    \chapter{Conclusions}
    	\input{chapters/conclusions}

   \appendix
   \chapter{Reference Equations}
    \input{chapters/appendix_A_equations}
    
    \chapter{Runge-Kutta Methods}
    \input{chapters/runge_kutta_methods}

    \bibliography{library}
    \end{document}








 









Documentation: 
    This style file modifies the standard report style to follow the
    Graduate Degree Support Section of the Registrar's Office's
    "Directions for Preparing Doctoral Dissertations".  It sets the
    margins and interline spacing and disallows page breaks at
    hyphens.

    The \beforepreface command creates the title page, a copyright page
    (optionally), and a signature page.  Then the user should put
    preface section(s), using the \prefacesection{section title}
    command.  The \afterpreface command then produces the tables of
    contents, tables and figures, and sets things up to start
    the main body (on arabic page 1).
    
    The following commands can control what goes in the front matter
    material:
    
        \title{thesis title}
        \author{author's name}
        \dept{author's department}
                - Computer Science if omitted
The following switches allow for special title pages (not all are current)
        \committeethesis - for a thesis in a committee (no dept.)
                           use \dept{committee name}
        \programthesis - for a thesis in a program (no dept.)
                           use \dept{program name}
        \educationthesis - for the School of Education. \dept doesn't matter
        \businessthesis - for the GraduateSchool of Business. \dept doesn't matter
        \lawthesis - for the School of law. \dept doesn't matter
        \humanitiesthesis - for a thesis also submitted to the Graduate
                            Program in Humanities
        \specialthesis  - for a Graduate Special thesis
        \industrialthesis - for a thesis in Industrial Engineering
        \dualthesis     - for a thesis in a dual language department.
                          Also define \languagemajor{language}.
                          e.g., \dept{French and Italian} 
                          \languagemajor{Italian}
         \principaladviser{the principal advisor's name}
           (or \principaladvisor, if you prefer advisor spelled with o)
        \coprincipaladviser{optional second principal advisor's name}
           (or \coprincipaladvisor, use only if you have two principal
           advisors only for the second one)
        \firstreader{the first reader's name}
        \secondreader{the second reader's name}
        \thirdreader{optional third reader's name}
        \fourthreader{optional fourth reader's name}
        \setlength{\signaturespace}{.5in} 
                - default is .5in, can be adjusted to fit all
                signatures in one page
        \submitdate{month year in which submitted to GPO}
                - date LaTeX'd if omitted
        \copyrightyear{year degree conferred (next year if submitted
          in Fall quarter)}
                - year LaTeX'd (or next year, in December) if omitted
        \copyrighttrue or \copyrightfalse
                - produce or don't produce a copyright page (true by default)
        \thesiscopyrighttrue or \thesiscopyrightfalse
                - produces the style of copyright page listed by the
                Thesis Office or the style that everyone else uses
                (Thesis office by default).
        \figurespagetrue or \figurespagefalse
                - produce or don't produce a List of Figures page
                  (true by default)
        \tablespagetrue or \tablespagefalse
                - produce or don't produce a List of Tables page
                  (true by default)

This style uses interline spacing that is 1.3 times normal, except
in the figure and table environments where normal spacing is used.
That can be changed by doing:
    \setstretch{1.6}
(or whatever you want instead of 1.6)

This command should be put before the \begin{document} command but
after loading the packages

You can also set any particular section in singlespacing mode by using
the singlespace environment.  For example

\begin{quote}
\begin{singlespace}
...
\end{singlespace}
\end{quote}

makes the quote singlespaced.  See the documentation for setspace.sty
for more information.

The example at the beginning shows the 12pt substyle being used.  This
seems to give acceptable looking results, but it may be omitted to get
smaller print.